Kindly Bent to Free Us

### 2019-06-29 kindly/main.tex
metatheory started
More motivations
semantics and metatheory
Attempt at typesetting code-as-semrules.
Progress on inference soundness proof.
abstract

% Math
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
% \usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{textcomp}
\usepackage{gensymb}
% \usepackage{textgreek}

@@

\usepackage{caption}
\usepackage{subcaption}

@@

\input{prelude}
\input{caml}
\input{notations}

@@

\title{Kindly Bent to Free Us}
\begin{abstract}
  System programming often requires to manipulate resources that
  cannot be duplicated such as file system handles, network connections,
  or globally allocated memory.
  Improper handling of such resources is often the cause of bugs and security issues
  through use-after-free errors or data races. These problems are not
  prevented by most statically typed programming languages that only
  guarantee type soundness and memory safety.
  Linear and affine type systems support tracking of single-threaded resource usage
  through types, but they are often too restrictive for real-world applications.

  We present \lang, an extension of ML with a kind system and qualified
  types that allows to track affine types.
  This language supports the defining features of ML family languages:
  an impure, strict functional expression language with complete principal type
  inference and type abstraction through modules.
  Our language do not require any linearity annotation in
  expressions and support common functional idioms.
\end{abstract}

@@

@@

\input{infer/infer}
\input{soa}

>>>>

% Math
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
% \usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{textcomp}
\usepackage{gensymb}
% \usepackage{textgreek}
\usepackage{multicol}

@@

\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}
%\setlist{leftmargin=*,noitemsep,topsep=5pt}

@@

\input{prelude}
\input{caml}
\input{lst-rule}
\input{notations}

@@

\title{Kindly Bent to Free Us}
\begin{abstract}
  System programming often requires the manipulation of resources like
  file system handles, network connections, or dynamically allocated
  memory. Programmers need to follow certain protocols to handle
  these resources correctly. Violating these protocols causes bugs
  ranging from type mismatches over data races to use-after-free 
  errors and memory leaks. These bugs often lead to security  vulnerabilities.

  Proper statically typed programming languages guarantee type soundness and memory 
  safety by design, but most of them do not address issues arising
  from improper resource handling. 
  Linear and affine types guarantee single-threaded resource usage,
  but they are rarely deployed as they are too restrictive for real-world applications.

  We present \lang, an extension of ML with constrained types that
  manages linearity and affinity properties through kinds. In addition
  \lang{} supports the mutable and immutable borrowing of affine
  resources, inspired by features of Rust.
  Moreover, \lang{} retains the defining features of the ML family:
  an impure, strict functional expression language with complete principal type
  inference and type abstraction through modules.
  Our language does not require any linearity annotations in
  expressions and supports common functional programming idioms.
\end{abstract}

@@

\input{rulemacros}

@@

\input{infer/infer}
\input{metatheory}
\input{soa}
